---
title: "regression problem"
author: "dr. J"
date: "2/16/2020"
output: html_document
---

# Introduction:
Data are from the website http://fueleconomy.gov 
This is a problem in modeling/prediction.
The idea is this:  Fuel efficiency from 2010 and 2011 passenger cars and light trucks is provied.  Using data from 2010, find the best model to predict fuel effiency; fit the model using data from 2010, and evaluate model performance using 2011 data.  

Questions:  
1. Is there evidence of an improvement in fuel efficiency from 2010 to 2011?  
2. What variables are most significant predictors of fuel efficienty?  
3. Suggest ways in which fuel efficienty could be improved in future years.  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(AppliedPredictiveModeling)
library(dplyr)
```

data set: fuel economy from US Gov't website

```{r}
data(FuelEconomy)
library(lattice)

```
### Plot shown in the text:

load the data
FE is fuel economy

```{r}
cars2010 <- cars2010[order(cars2010$EngDispl),]
cars2011 <- cars2011[order(cars2011$EngDispl),]
cars2010a <- cars2010
cars2010a$Year <- "2010 Model Year"
cars2011a <- cars2011
cars2011a$Year <- "2011 Model Year"
plotData <- rbind(cars2010a, cars2011a)
plotTheme <- bookTheme(FALSE)
plotTheme$plot.symbol$col <- rgb(.2, .2, .2, .5)
plotTheme$plot.symbol$cex <- 0.7
trellis.par.set(plotTheme)

xyplot(FE ~ EngDispl|Year, plotData,
xlab = "Engine Displacement",
ylab = "Fuel Efficiency (MPG)",
between = list(x = 1.2))

```

## difference in mean fuel efficiency 2010 to 2011

$H_0$: no difference between FE in 2010 and 2011  
$H_A$: there is a difference in FE for years 2010 and 2011

We'll use a t-test for this inference:

```{r}
t.test(cars2010a$FE, cars2011a$FE)
```
Question #1:
No evidence of any improvement/difference in mean FE between 2010 and 2011



### variables in the data set:

```{r}
names(cars2010a)
```

try transmissons = AV, AM6 and AM7

```{r}
testTranny = filter(cars2010a, Transmission %in% c('AV','AM7'))
trannyModel = glm(FE ~ Transmission, data = testTranny)
summary(trannyModel)

print(mean(testTranny$FE))

```

Try adding air asperation method to see what it does..

```{r}
levels(cars2010a$ExhaustValvesPerCyl)
trannyValveModel = glm(FE ~ Transmission + ExhaustValvesPerCyl, data = testTranny)
summary(trannyValveModel)
```

## ANOVA

```{r}

model1 = glm(FE~EngDispl+
              NumCyl +  
              AirAspirationMethod +
              TransCreeperGear +
              DriveDesc
    ,data=cars2010a)

summary(model1)

anova(model1)


```

It appears that TransCreeperGear is a drag, leave it out;
drive desc: front two wheel
```{r}
pruned2010a = filter(cars2010a, TransCreeperGear==0 &  DriveDesc=='TwoWheelDriveFront' & EngDispl < 3)

model2 = glm(FE~EngDispl, data=pruned2010a)

summary(model2)

anova(model2)


```



make a prediction for 2011


```{r}
pred2011 = predict(model2, cars2011a)
#print(pred2011)
hist(pred2011)
boxplot(pred2011, main='data from 2011\nmodelall')
```



## compare average fuel efficiency for 2011 cars using model1 to fuel efficiency for all cars in 2010

```{r}
t.test(cars2011a$FE, pred2011)
```


